Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-08-22 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Minor edits due to comments from Ran

We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a CFL condition, a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.  
Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.

@@

In this work, we considered a relatively simple model.  
In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background, isotropic elastic scattering, and relativistic effects due to interactions with a moving background or the presence of a strong gravitational field were not included.  
To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  
In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.

>>>>

We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a time step restriction (CFL condition), a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.  
Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.

@@

In this work, we considered a relatively simple model.  
In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background.  
Inelastic scattering and relativistic effects (e.g., due to interactions with a moving background or the presence of a strong gravitational field) were not included.  
To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  
In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.
